---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cah

<!-- badges: start -->
<!-- badges: end -->

The `cah` package contains useful tools for CAHers. The two main categories of tools are: tools that make statistical analysis easier, and tools that make collaboration easier. In addition, there's tools that help with research project coorination, etc.

## Installation

You can install the development version of cah from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("janlindemans/cah")
```

## Set up

<!-- COPY from vignette: edit original there -->


## Usage

<!-- COPY from vignette: edit original there -->


```{r example}
# copy paste from vignette
```

## Vignette

Check out the vignette for more examples on how to use the package.
