---
title: "cah"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cah}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
#devtools::build_rmd("vignettes/cah.Rmd")
```

## Set up

*If you followed the instructions when installing, you should have already set things up. Just in case you haven't yet, I'll repeat the set-up instructions here.*

For the `CAH Shared` folder in Box, and the `CAH` folder in Drive, set the options in your `.Rprofile` file - it will be used by several `cah` functions.

Something like this:

```{r, eval = FALSE}
options(
  cah.box_path = 
    "/Users/yourname/Library/CloudStorage/Box-Box/CAH/CAH Shared",
  cah.drive_path = paste0(
    "/Users/yourname/Library/CloudStorage/GoogleDrive-youremail@gmail.com/",
    ".shortcut-targets-by-id/somestring/CAH/CAH Shared Drive"
  )
)
```
```{r, include = FALSE}
options(
  cah.box_path = 
    "/Users/jwl38/Library/CloudStorage/Box-Box/CAH/CAH Shared",
  cah.drive_path = paste0(
    "/Users/jwl38/Library/CloudStorage/GoogleDrive-janwillem.lindemans@gmail.com/",
    ".shortcut-targets-by-id/1mCSu5zzZGk4BAPPBaZCMQXwnKmOPQSfU/CAH/CAH Shared Drive"
  )
)
```

If you haven't used `.Rprofile` before, it's a hidden file with code R runs at startup. It's located somewhere somewhere similar to this: `Users/johnwilliam/.Rprofile`. Learn more about `.Rprofile` on [the Posit Support page](https://support.posit.co/hc/en-us/articles/360047157094-Managing-R-with-Rprofile-Renviron-Rprofile-site-Renviron-site-rsession-conf-and-repos-conf).


## CAH paths

`cah` helps you with paths to commonly used files:

```{r}
library(cah)
cah_files()
cah_files(box)
cah_path(box)
```

Open the Box folder:

```{r eval = FALSE}
system2("open", shQuote(cah_path(box)))
```

Read a file:

```{r}
cah_files(projects_sheet)
cah_path(projects_sheet)
readxl::read_excel(cah_path(projects_sheet))
```

## Use the `better` package



```{r}
# cah makes it easy to use other libraries by helping set path options
#cah_set_options()
library(tidyverse)
library(better)

nudge_to_behavior(nudge = "structure", behavior = "health") 


vignette("better")
gbd_load()
gbd_list$gbd
```

The main purpose of `better` is to help you better guestimate the effect of health nudges, that is, behavioral interventions targeted at health behaviors. 

Imagine you are designing a public health campaign. You are thinking about focusing on preventing cardiovascular diseases, and you are considering making information about healthy lifestyle more accessible. What effects can you expect from a campaign like that? This is how we would do it with `better`.

First, we look up the effect of an information nudge on health behavior.

```{r}
library(tidyverse)
library(better)
nudge_to_behavior(nudge = "information", behavior = "health") 
```

This gives us a Cohen's *d*, a standardized effect size for the health information nudge, namely, *d* = `r nudge_to_behavior(nudge = "information", behavior = "health")$value`.

Second, as an intermediate step, we translate Cohen's *d* into a percentage point difference.

```{r}
nudge_to_behavior(nudge = "information", behavior = "health") %>%
  behavior_cd_to_pp
```

This gives us a decrease of `r nudge_to_behavior(nudge = "information", behavior = "health") %>% behavior_cd_to_pp %>% {round(abs(.$value),1)}` percentage points.

Finally, we can get our guestimate of the effect:

```{r}
nudge_to_behavior(nudge = "information", behavior = "health") %>%
  behavior_cd_to_pp %>%
  behavior_to_disease("cardiovascular diseases")
```

We learned something! If we're going to roll out an information nudge in 100,000 people, targeted at cardiovascular diseases, we're expected to boost disability adjusted life years by about `r nudge_to_behavior(nudge = "information", behavior = "health") %>% behavior_cd_to_pp %>% behavior_to_disease("cardiovascular diseases") %>% {round(.$value)}` years! That's not bad. 

Note that this is based on the following statistic:

```{r}
gbd_describe(cause = "cardiovascular diseases")
```

Let's see, what if we would shift the focus of our intervention to diabetes and kidney diseases?

```{r}
nudge_to_behavior(nudge = "information", behavior = "health") %>%
  behavior_cd_to_pp %>%
  behavior_to_disease("diabetes and kidney diseases")
```

What if we tried a structural nudge?

```{r}
nudge_to_behavior(nudge = "structure", behavior = "health") %>%
  behavior_cd_to_pp %>%
  behavior_to_disease("diabetes and kidney diseases")
```



```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
